\documentclass[a4paper,9pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.4in, bottom=0.4in]{geometry} % Tighter 
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol} % Multi-column format
\usepackage{enumitem} % Compact itemization

\setlength{\parindent}{0pt} % Remove indentation
\setlength{\parskip}{0pt} % Reduce paragraph spacing
\linespread{0.9} % Slightly tighter line spacing

\titleformat{\section}
  {\color{teal}\small\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\Large \textbf{Rafael Delwart}} \\
    {\small \textcolor{teal}{Robotics Engineer}} \\
    \vspace{0.3em}
    {\footnotesize
        4095 California St, San Francisco, CA 94118 \quad | \quad
        +1 (415) 802-5537 \quad | \quad
        \href{mailto:radelwart@gmail.com}{radelwart@gmail.com} \quad | \quad
        \href{https://ramfi-d.github.io/Website/}{ramfi-d.github.io/Website/}
    }
    \vspace{0.8em}
\end{center}

\section*{About Me}
 I am a Robotics Engineering graduate from UCSC, born and raised in San Francisco, with hands-on experience in microelectronics, programming microcontrollers, and automating complex systems. I am proficient in Kicad, C++, and SolidWorks, capable of simulating and developing real-world applications. I am a fast learner with practical expertise in leading a team, software development, electrical systems, and CAD design.\normalsize

\section*{Major Projects}

\small 

\textbf{Wet-Dry Cycler for RNA Production} \\
Recruited and led a team to design and build an automated system to simulate early Earth conditions for non-enzymatic RNA synthesis, supporting origins-of-life research in collaboration with Dr. David Deamer.

\textbf{3D Tracking Using an IMU for Rock Climbing} \\
Developed an inertial measurement unit (IMU)-based tracking system for analyzing climber movement, improving performance insights, and motion visualization.

\textbf{Mechatronics Competition (2nd Place)} \\
Led the development of a high-performance autonomous robotic system, integrating microcontrollers, sensors, and real-time feedback for competitive mechatronics tasks.

\textbf{Detailed descriptions and documentation available at: }\colorbox{yellow}{\href{https://ramfi-d.github.io/Website/}{\textbf{ramfi-d.github.io/Website/}}}

\section*{Work Experience}
\textbf{UCSC, Santa Cruz, CA} \\
\textit{Undergraduate Tutor — ECE167: Sensors and Sensing } \\
\textit{Supervisor: Professor Collen Josephson \href{mailto:cjosephson@ucsc.edu}{(cjosephson@ucsc.edu)}} \\[0.3em]
Led tri-weekly lab sessions for 100 plus students on sensor technologies and data processing. Covered sensing principles, calibration, signal filtering, ADC, and data acquisition. Guided students in practical lab applications using C programming and lab equipment.

\section*{Skills}
\small
\textbf{Programming:} Python, Kicad, C, C++, Verilog, MATLAB, Assembly, HTML, CSS, Latex. \\
\textbf{Math \& Physics:} Strong background in advanced concepts. \\
\textbf{Systems Modeling:} Kinematics, dynamics, SolidWorks, OnShape. \\
\textbf{Electronics:} LTSpice, Circuit design, analysis, analog/digital systems. \\
\textbf{Projects:} Microcontrollers, sensors, 3D prototyping, technical documentation. \\
\textbf{Languages:} Fluent in French and English.
\normalsize

\section*{Education}
\small
\textbf{University of California, Santa Cruz (UCSC)} \hfill \textit{Dean's Honor List (4 times)} \\
Robotics Engineering, Minor in Electrical Engineering \hfill \textit{Major GPA: 3.74} \\
Sept 2020 - June 2025 \hfill \textit{Honors Graduate in both fields}

\section*{References}
\footnotesize
\textbf{Prof. David Deamer} \href{mailto:deamer@soe.ucsc.edu}{(deamer@soe.ucsc.edu)} • \textbf{Prof. Collen Josephson} \href{mailto:cjosephson@ucsc.edu}{(cjosephson@ucsc.edu)} • \textbf{Prof. Zouheir Rezki} \href{mailto:zrezki@ucsc.edu}{(zrezki@ucsc.edu)}
\normalsize

\section*{Most Relevant Courses}
\small
\begin{multicols}{3}
    \textbf{Computer Science:} \\
    Logic Design \\
    Data Structures \\
    Probability \& Statistics \\
    Assembly \\
    Discrete Math \\
    Python \\
    Programming Abstractions \\
    C Programming \\

    \columnbreak
    \textbf{Electrical \& Mech. Engineering:} \\
    Project for Professor Deamer \\
    Applied Feedback Control \\
    Feedback Control Systems \\
    Analog Electronics \\
    Sensors \& Sensing \\
    Embedded Systems \\
    Mechatronics \\
    Signals \& Systems \\
    Circuits \\

    \columnbreak
    \textbf{Math \& Physics:} \\
    Statics \& Mechanics \\
    Calculus I \\
    Calculus II \\
    Linear Algebra \\
    Vector Calculus \\
    Physics I \\
    Physics III \\
    Mathematical Methods II \\
    Kinematics \\

\end{multicols}
\normalsize

\end{document}
\textbf{Prof. David Deamer} \href{mailto:deamer@soe.ucsc.edu}{(deamer@soe.ucsc.edu)} • \textbf{Prof. Collen Josephson} \href{mailto:cjosephson@ucsc.edu}{(cjosephson@ucsc.edu)} • \textbf{Prof. Zouheir Rezki} \href{mailto:zrezki@ucsc.edu}{(zrezki@ucsc.edu)}
\normalsize

\end{document}

